\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{charter}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{ragged2e}

\setlength{\columnsep}{20pt}
\title{Arranging a Gaming Tournament: A Step-By-Step Guide in \LaTeX}
\author{A Z Hasnain Kabir}
\date{January 29, 2024}

\begin{document}
	
	\maketitle
	
	\tableofcontents
	\newpage
	
	\begin{abstract}
		Organizing a gaming tournament is an exciting venture that demands careful planning and execution. This step-by-step guide takes you through the process, from setting clear objectives to post-event evaluation. Each step is meticulously detailed with nested itemized and enumerated lists, offering a comprehensive overview of tournament organization. Start by defining your goals and selecting the game, and delve into budgeting, venue selection, equipment setup, and promotion. Navigate rules and regulations, build a dedicated team, and manage the event seamlessly. Conclude with an awards ceremony and gather valuable feedback. Whether you’re a seasoned event planner or a first-time host, this guide provides a solid foundation for creating memorable gaming tournaments.
	\end{abstract}
	
	\section{Introduction}
	Organizing a gaming tournament can be an exhilarating and rewarding experience. Whether it’s a local eSports competition or a large-scale gaming event, careful planning and execution are essential for a successful tournament. This guide will walk you through the key steps to ensure that your gaming tournament runs smoothly and captivates both participants and spectators.
	
	\section{Steps to Organize a Gaming Tournament}
	\begin{multicols}{2}
	\begin{enumerate}
		\item \textbf{Define Your Goals}
		\begin{itemize}
			\item Determine the primary objectives of your tournament.
			\item Set clear and measurable goals.
		\end{itemize}
		\item \textbf{Choose the Game}
		\begin{enumerate}
			\item Select the video game or games.
			\item Decide on the tournament format.
		\end{enumerate}
		\item \textbf{Budget and Funding}
		\begin{itemize}
			\item Create a detailed budget.
			\item Explore funding options.
		\end{itemize}
		\item \textbf{Secure a Venue}
		\begin{enumerate}
			\item Find a suitable location.
			\item Ensure the venue has the necessary facilities.
		\end{enumerate}
		\item \textbf{Equipment and Setup}
		\begin{itemize}
			\item Rent or acquire gaming consoles, PCs, monitors, and other equipment.
			\item Set up the gaming stations.
		\end{itemize}
		\item \textbf{Registration and Promotion}
		\begin{enumerate}
			\item Create an online registration system.
			\item Develop a marketing plan.
		\end{enumerate}
		\item \textbf{Rules and Regulations}
		\begin{itemize}
			\item Establish clear and fair rules for the tournament.
			\item Communicate these rules to participants.
		\end{itemize}
		\item \textbf{Staffing and Volunteers}
		\begin{enumerate}
			\item Recruit a team of volunteers and staff members.
			\item Provide adequate training to your team.
		\end{enumerate}
		\item \textbf{Execution and Management}
		\begin{itemize}
			\item Execute the tournament according to the established schedule.
			\item Continuously monitor the event.
		\end{itemize}
		\item \textbf{Awards and Closing Ceremony}
		\begin{enumerate}
			\item Plan an awards ceremony.
			\item Thank sponsors, volunteers, and participants.
		\end{enumerate}
		\item \textbf{Evaluation and Feedback}
		\begin{itemize}
			\item Collect feedback from participants and staff.
			\item Assess the achievement of your initial goals.
		\end{itemize}
	\end{enumerate}
	\end{multicols}
	
	\section{Conclusion}
	Arranging a gaming tournament is a thrilling endeavor that requires careful planning, dedication, and teamwork. By following these steps and staying adaptable, you can create an unforgettable gaming experience for all involved. Whether you’re a seasoned event organizer or a first-time tournament host, this guide will help you navigate the exciting world of competitive gaming events.
	
	\section{Acknowledgment in Verse}
	\begin{center}
			\itshape
			In the realm of gaming, we set our sights high, \\
			With gratitude and warmth, our hearts touch the sky. \\
			
			To the gamers, the dreamers, and those who play, \\
			Your passion and spirit light our way every day. \\
			
			To our families and friends, our guiding starlight, \\
			Your support and love are our source of delight. \\
			
			To the open-source community, we tip our hat, \\
			Your tools and your wisdom, where would we be at? \\
			
			And to you, dear reader, who explores our guide, \\
			Your curiosity and interest give us great pride. \\
			
			In this verse, we acknowledge, with hearts full and free, \\
			The gamers, the dreamers, who helped us to see.

	\end{center}
	
	\section{Secrets}
	\begin{itemize}
		\item Paper size is A4
		\item Margin is 0.75 inch all around
		\item Font size is 11 pt
		\item \texttt{charter} is set as font
		\item \texttt{multicol} package with 20pt column separation is used for two column format
		\item Do not forget to use \texttt{hyperref}
		\item \texttt{ragged2e} contributed to the beautifully centered acknowledgement section.
		\item Try to figure out how the code-style or \texttt{teletype} fonts are printed.
	\end{itemize}
\end{document}
